---
title: "Dhaka UGS Use ParkRx"
output: html_document
---

This is R Markdown document to provide the modelling conducted to analyse the Urban greenspace usage in Dhaka.

Loading the packages used in this study
```{r load packages}

library(rmarkdown)
library(MASS)
library(car)
library(rcompanion)
library(mediation)

```

## Load the data (CSV) file and convert it into data object

```{r load data}
park_data <- read.csv(file.choose())
pdata <- park_data
```

## Modelling the UGS use intentsity: Model-1(Base Model)

```{r model-1}
#UGSmodelbase (Model-1)
UGSmodelbase <- glm(UseIntensity~ gender+ edu+ emplF+ TrMode + GSPc +Attractiveness + Accessibility + Attachment, family = binomial(link='logit'), data= pdata)
summary(UGSmodelbase)
#Odds ratio
exp(coef(UGSmodelbase))
#odds ratio 95% CI
exp(confint(UGSmodelbase))
#model-1 fit details
nagelkerke(UGSmodelbase)
vif(UGSmodelbase)

```

# Modelling the UGS use intentsity: Model-2(Base Model and NCDs/Chronic)

```{r model-2}
#UGSmodelbase + NCDs/Chronic (Model-2)
UGSmodelNCDs <- glm(UseIntensity~ gender+ edu+ emplF+ TrMode + GSPc +Attractiveness + Accessibility + Attachment + NCDs, family = binomial(link='logit'), data= pdata)
summary(UGSmodelNCDs)
#Odds ratio
exp(coef(UGSmodelNCDs))
#odds ratio 95% CI
exp(confint(UGSmodelNCDs))
#model-2 fit details
nagelkerke(UGSmodelNCDs)
vif(UGSmodelNCDs)

```

# Modelling the UGS use intentsity: Model-3(Base Model and ParkRx)
```{r model-3}
#UGSmodelbase + ParkRx (Model-3)
UGSmodelParkRx <- glm(UseIntensity~ gender+ edu+ emplF+ TrMode + GSPc +Attractiveness + Accessibility + Attachment + ParkRx, family = binomial(link='logit'), data= pdata)
summary(UGSmodelParkRx)
#Odds ratio
exp(coef(UGSmodelParkRx))
#odds ratio 95% CI
exp(confint(UGSmodelParkRx))
#model-3 fit details
nagelkerke(UGSmodelParkRx)
vif(UGSmodelParkRx)
```


#Fit models for mediation analyses
```{r fitting full models for mediation}

#direct relationship between mediatior and predictor variable (ParkRx is the mediator and Chronic is the predictor) model 4
med.ParkRx <- glm (ParkRx ~ NCDs + GSPc +Attractiveness + Accessibility + Attachment +gender+ edu+ emplF+ TrMode, family = binomial(link='logit'), data= pdata)
summary(med.ParkRx)
#Odds ratio
exp(coef(med.ParkRx))
#odds ratio 95% CI
exp(confint(med.ParkRx))
#model-2 fit details
nagelkerke(med.ParkRx)


#intensity full model (model 5)
Outputmodel5 <- glm(UseIntensity~ gender+ edu+ emplF+ TrMode + GSPc +Attractiveness + Accessibility + Attachment + NCDs + ParkRx, family = binomial(link='logit'), data= pdata)
summary(Outputmodel5)
#Odds ratio
exp(coef(Outputmodel5))
#odds ratio 95% CI
exp(confint(Outputmodel5))
#model-2 fit details
nagelkerke(Outputmodel5)


```



#UGS Use intensity, NCDs and ParkRx mediation
```{r mediation for intensity}
#mediation between the full fit model and mediator model
set.seed (123)
med.output <- mediate(med.ParkRx, Outputmodel5, treat = "NCDs", mediator = "ParkRx", robustSE = TRUE, sims = 1000)
summary(med.output)
plot(med.output, main = "UGS intensity of use mediation effects of ParkRx on NCDs", col="black", xlab="Effect Size")
```


#Notes: ACME- average causal mediation effect; ADE- average direct effect; Total effect = ACME + ADE


